Activity Dataset
========================================================
Load the 'Activity Dataset' and necessary libraries
```{r,echo=TRUE}
library(ggplot2)
library(dplyr)
activity<-read.csv('activity.csv')
```
group by date
```{r,echo=TRUE}
comp_activity<-na.omit(activity)
dailystep<-group_by(comp_activity,date)%>%summarize(step=sum(steps))
dailystep
```
plot histogram
```{r fig.height=7,fig.width=6,echo=TRUE}
qplot(step, bins=30, data=dailystep)
```


mean of steps taken per day

```{r,echo=TRUE}
mean(dailystep$step)
```

median of steps taken per day
```{r,echo=TRUE}
median(dailystep$step)
```
group steps by interval

```{r  fig.height=7,fig.width=6,echo=TRUE}
mean_step_per_interval<-group_by(comp_activity, interval)%>%summarize(step=mean(steps))
```

Time series plot of interval against step

```{r,echo=TRUE}
plot<-ggplot(mean_step_per_interval, aes(y=step,x=interval))+geom_line()+labs(title='Interval againt time')
plot
```
5-minute interval with maximum steps

```{r,echo=TRUE}
mean_step_per_interval$interval[which.max(mean_step_per_interval$step)]
```
##IMPUTING MISSING VALUES##
=============================

total missing values(NA)

```{r,echo=TRUE}
sum(is.na(activity))
```

Replace missing values with the mean steps for that 5-mins Interval


```{r, echo=TRUE}
act.copy<-activity
for (i in seq(nrow(act.copy))) {
  if (is.na(act.copy[i,1])) {
    intvl<-act.copy[i,3]
    act.copy[i,1]<-round(subset(mean_step_per_interval,interval==intvl,step),3)
  }
}
sum(is.na(act.copy))
dim(act.copy)
```

Histogram of total steps taken after imputation

```{r fig.height=7,fig.width=6}
steps.day<-group_by(act.copy,date)%>%summarize(steps.per.day=sum(steps))
head(steps.day,8)
qplot(steps.per.day,  data=steps.day)
```

##Mean Steps per day after imputation##
```{r,echo=TRUE}
mean(steps.day$steps.per.day)
```

##median steps per day after imputation##
```{r,echo=TRUE}
median(steps.day$steps.per.day)
```

**Convert date variable using as.Date function
```{r,echo=TRUE}
act.copy$day<-weekdays(as.Date(act.copy$date,'%Y-%m-%d'))
head(act.copy)
```

**Group days into weekdays and weekends**

```{r,echo=TRUE}
act.copy$weektype<-ifelse(act.copy$day %in% c('Saturday','Sunday'),'weekend','weekday')
act.copy$weektype<-as.factor(act.copy$weektype)
head(act.copy,10)
```

**Calculate mean daily step per 5-min interrval for all days**

```{r,echo=TRUE}
r<-act.copy%>%group_by(interval,weektype)%>%summarize(mean.step=mean(steps))
class(act.copy$weektype)
head(r)
```

*PANEL PLOT OF WEEKEND AND WEEKDAY MEAN STEPS*

```{r fig.height=6,fig.width=10,echo=TRUE}
p<-ggplot(r, aes(x=interval,y=mean.step))+geom_line()+facet_grid(.~weektype)
p
```




